---
title: "Projects"
author: "Nathan Angell"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

Hello my name is Nathan Angell and I am a senior at Bryant University. For the past 3 and a half years I have been a data scientist working on many different projects. These projects have been through school, internships, and personal projects. Here is a highlight of most of the projects I did to showcase my skills I have learned these past couple of years. 

## Introduction to Programming (ISA 221)

For my first programming class, I started with no knowledge on how to code in python. Eventually, as the class and I started to dive into the book slowly but surely worked our way up to this simple program. This [program](ISA_221 start program.html) is able to take a list of 20 numbers and find the min, max, total, and average. 

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
